Global study of well-being and internet adoption | Online analysis supplement

### 2021-11-18 03-analysis.Rmd
Reorganise analyses

```{r packages}
#| results: 'hide'
# Packages
library(ggtext)
library(brms)
library(cmdstanr)
library(ellipse)
library(broom.mixed)
library(scales)
library(ggh4x)
library(tidybayes)
library(ggdist)
library(posterior)
library(parameters)
library(lme4)
library(emmeans)
library(patchwork)
library(bayestestR)
library(lubridate)
library(broom)
library(kableExtra)
library(ggstance)
library(multidplyr)
library(tidyverse)

@@

## OLD

### brms

correlating temporal trends in outcomes and internet use using multilevel model with shared correlation matrix

note we use beta so transform edge values

we start with non interactive model--demographics are covariates. later to be expanded to interaction but slow

##### Time: Main effects

We first fit a multivariate model of time effects on internet penetration and each of the well-being outcomes.

```{r}
# Define a model of internet proportion over time
bf_int <- bf(
  internet ~ 1 + time + 
    (1 + time |c| country) +
    (1 + time |r| region), 
  family = Beta()
)

# Define models of outcomes
bf_anx <- bf(
  Anxiety ~ 1 + time + sex + age + 
    (1 + time + sex + age |c| country) +
    (1 + time + sex + age |r| region),
  family = gaussian()
)
bf_dep <- bf(
  Depression ~ 1 + time + sex + age + 
    (1 + time + sex + age |c| country) +
    (1 + time + sex + age |r| region),
  family = gaussian()
)
bf_sel <- bf(
  Selfharm ~ 1 + time + sex + age + 
    (1 + time + sex + age |c| country) +
    (1 + time + sex + age |r| region),
  family = gaussian()
)

# Fit models
fit_anx <- brm(
  bf_int + bf_anx + set_rescor(FALSE),
  data = dat_10,
  file = "output/brm-gbd-time-anxiety",
  chains = 4,
  cores = 4,
  iter = hmc$iter, warmup = hmc$warmup, 
  control = list(adapt_delta = hmc$d)
)
fit_dep <- brm(
  bf_int + bf_dep + set_rescor(FALSE),
  data = dat_10,
  file = "output/brm-gbd-time-depression",
  chains = 4,
  cores = 4,
  iter = hmc$iter, warmup = hmc$warmup, 
  control = list(adapt_delta = hmc$d)
)
fit_sel <- brm(
  bf_int + bf_sel + set_rescor(FALSE),
  data = dat_10,
  file = "output/brm-gbd-time-selfharm",
  chains = 4,
  cores = 4,
  iter = hmc$iter, warmup = hmc$warmup, 
  control = list(adapt_delta = hmc$d)
)
fits_brm_time_main <- tibble(
  outcome = c("Anxiety", "Depression", "Selfharm"),
  fit = list(fit_anx, fit_dep, fit_sel)
)
```

```{r}
fits_brm_time_main %>% 
  mutate(
    out = map(
      fit, 
      ~as_draws(.x, variable = "b_", regex = TRUE) %>% 
        summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95)))
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  # filter(str_detect(Parameter, "_time$")) %>% 
  kbl(digits = 3) %>% 
  kable_minimal(full_width = FALSE)
```

Revisit figure of temporal trends with coefficients. Note we back-transform the estimated numbers to rates in 100,000

```{r}
tmp_pars <- fits_brm_time_main %>% 
  mutate(
    out = map2(
      fit, 
      outcome,
      ~hypothesis(
        .x, 
        c(str_glue("{.y}_time = 0")),
        scope = "coef",
        group = "region"
      )$hypothesis
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  # Internet trend is estimated in all models--keep first
  distinct(Group, Hypothesis, .keep_all = TRUE) %>% 
  # Transform back to rates in 100k
  mutate(across(where(is.numeric), ~round(.*1000, 0))) %>% 
  mutate(result = str_glue('**{Estimate}** [{CI.Lower}, {CI.Upper}]')) %>% 
  select(cause = Hypothesis, region = Group, result) %>% 
  mutate(cause = str_sub(cause, 2, -6) %>% str_remove("_time"))

p_vars +
  geom_richtext(
    data = tmp_pars %>% mutate(cause = fct_inorder(str_to_title(cause))),
    aes(x = make_date(2000), y = Inf, label = result),
    size = 2.2, vjust = .9, hjust = 0.1, color = "dodgerblue4",
    family = Font,
    fill = NA, label.color = NA
  )
ggsave(
  "output/Fig-vars-timeseries-estimates.png", 
  device = agg_png,
  height = 2400, width = 3600, res = 300, units = "px"
)
```

A figure of coefficients

```{r}
anx_draws <- spread_draws(
  fit_anx, 
  b_Anxiety_time, r_region__Anxiety[region, term] | region
) %>% 
  filter(term == "time") %>% 
  ungroup() %>% 
  select(-term) %>% 
  rename(Average = b_Anxiety_time) %>% 
  mutate(outcome = "Anxiety")
dep_draws <- spread_draws(
  fit_dep, 
  b_Depression_time, r_region__Depression[region, term] | region
) %>% 
  filter(term == "time") %>% 
  ungroup() %>% 
  select(-term) %>% 
  rename(Average = b_Depression_time) %>% 
  mutate(outcome = "Depression")
sel_draws <- spread_draws(
  fit_sel, 
  b_Selfharm_time, r_region__Selfharm[region, term] | region
) %>% 
  filter(term == "time") %>% 
  ungroup() %>% 
  select(-term) %>% 
  rename(Average = b_Selfharm_time) %>% 
  mutate(outcome = "Selfharm")

p_time_main_coefs <- bind_rows(anx_draws, dep_draws, sel_draws) %>% 
  mutate(across(Africa:Southern.Asia, ~.+Average)) %>% 
  pivot_longer(Average:Southern.Asia, names_to = "region") %>% 
  mutate(region = fct_relevel(factor(region), "Average")) %>% 
  mutate(outcome = factor(outcome)) %>% 
  mutate(is_average = region == "Average") %>% 
  mutate(region = str_replace(region, "\\.", " ")) %>% 
  mutate(region = if_else(region=="Average", "**Average**", region)) %>% 
  ggplot(aes(value, region, fill = is_average, alpha = is_average)) +
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
  scale_alpha_manual(values = c(.5, .9)) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_x_continuous("Linear trend", breaks = pretty_breaks()) +
  stat_halfeye(
    point_interval = NULL, normalize = "panels"
  ) +
  facet_wrap("outcome", nrow = 1, scales = "free_x") +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_markdown(),
    legend.position = "none"
  )
p_time_main_coefs
```

###### Correlations

@@

```{r time-correlation-anxiety}
# Function to wrangle draws at multiple levels and create scatterplots + ellipses
draw_scatterplot <- function(fit, beta, r_region, r_country, sd_country, cor_country) {
  # Get average and region-specific slopes
  r_region_draws <- fit %>% 
    spread_draws(
      {{beta}}, 
      b_internet_time,
      {{r_region}}[region, term],
      r_region__internet[region, term]
    ) %>% 
    filter(term == "time") %>% 
    ungroup() %>% 
    # Fix names by replacing dot with line break
    mutate(region = str_replace(region, "\\.", "\n"))

  # Then country
  r_country_draws <- fit %>% 
    spread_draws(
      {{r_country}}[country, term],
      r_country__internet[country, term]
    ) %>% 
    filter(term == "time") %>% 
    ungroup() %>% 
    # Fix names by taking labels from original names
    mutate(
      country = factor(
        country, 
        labels = sort(unique(fit$data$country))
      )
    ) %>% 
    left_join(distinct(dat, region, country))

  # Calculate country coefficients
  country_coefs <- left_join(r_country_draws, r_region_draws) %>% 
    mutate(
      internet = b_internet_time + r_region__internet + r_country__internet,
      outcome = {{beta}} + {{r_region}} + {{r_country}}
    ) %>% 
    group_by(country, region) %>% 
    median_qi(internet, outcome)

  # Create country ellipse data
  country_ellipse <- spread_draws(
    fit,
    {{beta}}, 
    b_internet_time,
    {{sd_country}},
    sd_country__internet_time,
    {{cor_country}}, 
    ndraws = 100
  ) %>% 
    rename(
      cor = {{cor_country}}, 
      sd_outcome = {{sd_country}},
      sd_i = sd_country__internet_time,
      b_outcome = {{beta}},
      b_i = b_internet_time
    ) %>% 
    mutate(
      e = pmap(
        list(cor, sd_outcome, sd_i, b_outcome, b_i), 
        function(cor, sd_a, sd_i, b_a, b_i) 
          ellipse(
            cor, 
            scale = c(sd_i, sd_outcome), 
            centre = c(b_i, b_outcome), 
            level = .90
          ) %>% 
          as_tibble()
      )
    ) %>% 
    unnest(e)

  # Correlation
  country_cor_result <- spread_draws(fit, {{cor_country}}) %>% 
    median_qi(.width = .90) %>% 
    mutate(across(where(is.numeric), ~round(., 2))) %>%
    {str_glue("{.[,1]} [{.[,2]}, {.[,3]}]")}

@@

```{r}
p_cor_country_anx <- draw_scatterplot(
  fit_anx, 
  b_Anxiety_time, 
  r_region__Anxiety, 
  r_country__Anxiety,
  sd_country__Anxiety_time,
  cor_country__internet_time__Anxiety_time
) + labs(y = "Anxiety trend")
p_cor_country_dep <- draw_scatterplot(
  fit_dep, 
  b_Depression_time, 
  r_region__Depression, 
  r_country__Depression,
  sd_country__Depression_time,
  cor_country__internet_time__Depression_time
) + labs(y = "Depression trend")
p_cor_country_sel <- draw_scatterplot(
  fit_sel, 
  b_Selfharm_time, 
  r_region__Selfharm, 
  r_country__Selfharm,
  sd_country__Selfharm_time,
  cor_country__internet_time__Selfharm_time
) + labs(y = "Self-harm trend")
```

```{r}
p_time_main_correlations <- (p_cor_country_anx |
                               p_cor_country_dep |
                               p_cor_country_sel) &
  # Transform to rate in 100k
  scale_y_continuous(labels = function(x) x*1000)

@@

##### Time: Interactions

```{r}
# Define models of outcomes
bf_anx <- bf(
  Anxiety ~ 1 + time * sex + time * age + 
    (1 + time * sex + time * age |c| country) +
    (1 + time * sex + time * age |r| region),
  family = gaussian()
)
bf_dep <- bf(
  Depression ~ 1 + time + sex + age + 
    (1 + time * sex + time * age |c| country) +
    (1 + time * sex + time * age |r| region),
  family = gaussian()
)
bf_sel <- bf(
  Selfharm ~ 1 + time + sex + age + 
    (1 + time * sex + time * age |c| country) +
    (1 + time * sex + time * age |r| region),
  family = gaussian()
)

# Fit models
fit_anx <- brm(
  bf_int + bf_anx + set_rescor(FALSE),
  data = dat_10,
  file = "output/brm-gbd-time-anxiety-int2",
  chains = 4,
  cores = 4,
  iter = hmc$iter, warmup = hmc$warmup, 
  control = list(adapt_delta = hmc$d)
)
fit_dep <- brm(
  bf_int + bf_dep + set_rescor(FALSE),
  data = dat_10,
  file = "output/brm-gbd-time-depression-int2",
  chains = 4,
  cores = 4,
  iter = hmc$iter, warmup = hmc$warmup, 
  control = list(adapt_delta = hmc$d)
)
fit_sel <- brm(
  bf_int + bf_sel + set_rescor(FALSE),
  data = dat_10,
  file = "output/brm-gbd-time-selfharm-int2",
  chains = 4,
  cores = 4,
  iter = hmc$iter, warmup = hmc$warmup, 
  control = list(adapt_delta = hmc$d)
)
fits_brm_time_interactions <- tibble(
  outcome = c("Anxiety", "Depression", "Selfharm"),
  fit = list(fit_anx, fit_dep, fit_sel)
)
```

@@

```{r}
fits_brm_time_interactions %>% 
  mutate(
    out = map(
      fit, 
      ~as_draws(.x, variable = "b_", regex = TRUE) %>% 
        summarise_draws(quantile, rhat, .args = list(probs = c(.05, .5, .95)))
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  # filter(str_detect(Parameter, "_time$")) %>% 
  kbl(digits = 2) %>% 
  kable_minimal(full_width = FALSE)
```

Model comparison using waic shows that interactive model is favored across the board.

```{r eval = FALSE}
waics <- left_join(
  rename(fits_brm_time_main, fit_main = fit),
  rename(fits_brm_time_interactions, fit_intr = fit)
) %>% 
  mutate(waic = map2(fit_main, fit_intr, ~waic(.x, .y)))
waics$waic[[3]]
```

Show main effects

Plot fixed effects and by demographic

```{r}
# Fixed effects parameters
fixed_effects <- fits_brm_time_interactions %>% 
  mutate(out = map(fit, ~tidy(., conf.int = TRUE))) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  standardize_names() %>% 
  as_tibble() %>% 
  filter(
    Effects == "fixed", 
    Parameter != "(Intercept)"
  ) 
# Fixed effects per demographic
fixed_effects_demographics <- fits_brm_time_interactions %>% 
  mutate(
    out = map2(
      fit, outcome,
      ~emtrends(
        .x, 
        var = "time", 
        by = c("sex", "age"), 
        resp = .y
      ) %>% 
        parameters() %>% 
        as.data.frame()
    )
  )
fixed_effects_demographics %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  standardize_names() %>% 
  as_tibble() %>% 
  mutate(Parameter = str_glue("{sex}\n({age})"))

# Random effects parameters
random_effects <- fits_lmer %>% 
  mutate(
    coef_region = map(
      fit, 
      ~bind_rows(
        coef(.x)$region %>% 
          as.data.frame() %>% 
          rownames_to_column("region"),
        coef(.x)$country %>% 
          as.data.frame() %>% 
          rownames_to_column("country"),
        .id = "cluster"
      ) %>% 
        mutate(cluster = factor(cluster, labels = c("region", "country")))
    )
  ) %>% 
  select(-fit) %>% 
  unnest(coef_region) %>% 
  mutate(Type = "Effects") %>%
  select(-`(Int      ,nc ercept)`)

bind_rows(
  fixed_effects,
  fixed_effects_demographics, 
  .id = "Type"
) %>% 
  mutate(Type = factor(Type, labels = c("Effects", "Time by demographic"))) %>% 
  mutate(Parameter = fct_inorder(Parameter)) %>%
  mutate(cause = factor(cause)) %>% 
  rowwise() %>% 
  mutate(
    sig = factor(
      !between(0, CI_low, CI_high), 
      levels = c(TRUE, FALSE)
    )
  ) %>% 
  ggplot(aes(Coefficient, Parameter, col = cause, shape = sig)) +
  scale_color_discrete(
    "Outcome"
  ) +
  scale_x_continuous(
    "Estimate (95%CI)"
  ) +
  scale_shape_manual(values = c(19, 21)) +
  geom_vline(xintercept = 0, size = .2, alpha = .2) +
  geom_pointrangeh(
    aes(xmin = CI_low, xmax = CI_high),
    position = position_dodge2v(.5),
    fill = "white", size = .3, fatten = 5
  ) +
  guides(shape = "none") +
  facet_wrap("Type", ncol = 2, scales = "free") +
  theme(axis.title.y = element_blank())
```

```{r}
library(modelbased)
x <- parameters(fits_brm$fit[[1]], test = "pd", effects = "random", group_level = TRUE, keep = "time_Intercept")
tmp <- fits_brm %>% 
  mutate(
    # Average effect
    avg = map2(
      fit, 
      Outcome, 
      ~hypothesis(.x, str_glue("{.y}_time = 0"))
    ),
    # By country effect
    by_country = map2(
      fit, 
      Outcome, 
      ~hypothesis(
        .x, str_glue("{.y}_time = 0"), 
        scope = "coef", group = "country"
      )
    ),
    # By region effect
    by_region = map2(
      fit, 
      Outcome, 
      ~hypothesis(
        .x, str_glue("{.y}_time = 0"), 
        scope = "coef", group = "region"
      )
    )
  ) %>% 
  select(-fit)

tmp %>% 
  select(Outcome, avg) %>% 
  mutate(avg = map(avg, ))

tmp$by_region[[1]] %>% str

h <- paste(
  c("valAnxiety_Time", "valDepression_Time", "valSelfharm_Time"), 
  "= 0"
)

# Prepare average samples
time_avg <- hypothesis(fit_gbd_time, h)
time_avg_samples <- time_avg$samples
names(time_avg_samples) <- time_avg$hypothesis$Hypothesis
time_avg_samples <- time_avg_samples %>% 
  pivot_longer(everything(), names_to = "Parameter") %>% 
  mutate(region = "Average")

# Prepare region samples
time_region <- hypothesis(fit_gbd_time, h, scope = "coef", group = "region")
time_region_samples <- time_region$samples
names(time_region_samples) <- paste(
  time_region$hypothesis$Hypothesis, 
  time_region$hypothesis$Group, sep = ":"
)
time_region_samples <- time_region_samples %>% 
  pivot_longer(everything(), names_to = "Parameter") %>% 
  separate(Parameter, c("Parameter", "region"), sep = ":")

# Prepare country point estimates
time_country <- hypothesis(fit_gbd_time, h, scope = "coef", group = "country")
time_country_hypothesis <- time_country$hypothesis %>% 
  rename(country = Group, Parameter = Hypothesis)
time_country_hypothesis <- left_join(
  time_country_hypothesis, 
  distinct(fit_gbd_time$data, country, region)
)

time_sum <- bind_rows(
  time_region$hypothesis,
  time_avg$hypothesis %>% mutate(Group = "Average")
) %>% 
  as_tibble() %>% 
  rename(region = Group, Parameter = Hypothesis)

bind_rows(
  time_region_samples,
  time_avg_samples
) %>% 
  mutate(region = fct_relevel(region, "Average")) %>% 
  mutate(Average = region == "Average") %>% 
  ggplot(aes(value/10, region)) +
  scale_y_discrete(
    expand = expansion(c(0.025, 0.075)),
    labels = function(x) ifelse(x == "Average", "**Average**", x)
  ) +
  scale_x_continuous(
    "Estimated yearly change",
    breaks = pretty_breaks(5)
  ) +
  scale_alpha_manual(values = c(.5, 1)) +
  geom_vline(xintercept = 0, size = .2, alpha = .25) +
  stat_eye(
    side = "top",
    aes(col = region, fill = region, alpha = Average),
    point_interval = NULL,
    normalize = "panels", 
    height = .75
  ) +
  geom_pointrangeh(
    data = time_sum,
    aes(x = Estimate/10, xmin = CI.Lower/10, xmax = CI.Upper/10),
    size = .3, fatten = 1.4
  ) +
  geom_point(
    data = time_country_hypothesis,
    aes(col = region, x = Estimate/10), 
    size = .5,
    alpha = .25,
    position = position_nudge(y = -.05)
  ) +
  facet_wrap(
    "Parameter", ncol = 3, scales = "free_x",
    labeller = as_labeller(
      function(x) str_extract(x, "Anxiety|Depression|Selfharm"))
  ) +
  theme(
    axis.text.y = element_markdown(),
    legend.position = "none",
    axis.title.y = element_blank()
  )
ggsave(
  "output/Fig-brm-time-forest.png", 
  device = agg_png,
  height = 1200, width = 3200, res = 300, units = "px"
)
```

>>>>

```{r packages}
#| results: 'hide'
# Packages
library(ggtext)
library(brms)
library(cmdstanr)
library(ellipse)
library(broom.mixed)
library(scales)
library(ggh4x)
library(tidybayes)
library(ggdist)
library(posterior)
library(parameters)
library(lme4)
library(emmeans)
library(patchwork)
library(bayestestR)
library(lubridate)
library(broom)
library(kableExtra)
library(ggstance)
library(tidyverse)

@@

### Figure: Timecourses and parameters

```{r}

tmp_coefs <- fits_1c %>% 
  mutate(
    out = map(
      fit, 
      ~hypothesis(
        .x, 
        # Rescale coefficient here to years on %
        c(str_glue("val_year = 0")),
        scope = "coef",
        group = "region"
      )$hypothesis
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  mutate(across(where(is.numeric), ~round(., 2))) %>% 
  mutate(result = str_glue('**{Estimate}** [{CI.Lower}, {CI.Upper}]')) %>% 
  select(cause, region = Group, result)
tmp_coefs
pseudo_gwp <-
  bind_rows(
    distinct(gbd, region, year, val = NA) %>% 
      crossing(
        cause = fct_inorder(
          c(
            "Negative\nexperiences", 
            "Positive\nexperiences", 
            "Life\nsatisfaction"
          )
        )
      )
  )

# Stack data sets
# Assume all outcomes are proportions (0-1)
dat_all <- bind_rows(
  pseudo_gwp,
  gbd,
  itu %>% mutate(cause = "Internet", val = internet)
) %>% 
  mutate(cause = fct_inorder(cause)) %>% 
  group_by(region, country, year, cause) %>% 
  summarise(mean = mean(val, na.rm = TRUE)) %>% 
  ungroup()

# Draw small multiples figure, outcomes x regions
dat_all %>% 
  mutate(year = make_date(year)) %>% 
  ggplot(aes(year, mean)) +
  scale_y_continuous(
    "Value",
    labels = function(x) percent(x, .01) %>% str_remove("\\.00"),
    breaks = pretty_breaks()
  ) +
  scale_x_date(
    "Year",
    breaks = make_date(c(2000, 2005, 2010, 2015)), 
    date_labels = "'%y", 
    expand = expansion(.02)
  ) +
  geom_line(
    aes(group = interaction(country, cause)), 
    alpha = .25, size = .4, color = "dodgerblue1"
  ) +
  stat_summary(
    fun = mean, geom = "line", 
    size = .6, color = "dodgerblue4"
  ) +
  facet_grid(cause~region, scales = "free_y") +
  theme(
    legend.position = "none",
    panel.spacing = unit(3, "pt")
  ) +
  geom_richtext(
    data = tmp_coefs %>% mutate(cause = fct_inorder(str_to_title(cause))),
    aes(x = make_date(2000), y = Inf, label = result),
    size = 2.2, vjust = .9, hjust = 0.1, color = "dodgerblue4",
    family = Font,
    fill = NA, label.color = NA
  )
```

### Figure: Correlations

@@

```{r time-correlation-anxiety}
# Function to wrangle draws at multiple levels and create scatterplots + ellipses
draw_scatterplot <- function(fit, beta, r_region, r_country, sd_country, cor_country) {
  # Get average and region-specific slopes
  r_region_draws <- fit %>% 
    spread_draws(
      b_val_year, 
      b_internet_year,
      r_region__val[region, term],
      r_region__internet[region, term]
    ) %>% 
    filter(term == "year") %>% 
    ungroup() %>% 
    # Fix names by replacing dot with line break
    mutate(region = str_replace(region, "\\.", "\n"))

  # Then country
  r_country_draws <- fit %>% 
    spread_draws(
      r_country__val[country, term],
      r_country__internet[country, term]
    ) %>% 
    filter(term == "year") %>% 
    ungroup() %>% 
    # Fix names by taking labels from original names
    mutate(
      country = factor(
        country, 
        labels = sort(unique(fit$data$country))
      )
    ) %>% 
    left_join(distinct(dat, region, country))

  # Calculate country coefficients
  country_coefs <- left_join(r_country_draws, r_region_draws) %>% 
    mutate(
      internet = b_internet_year + r_region__internet + r_country__internet,
      outcome = b_val_year + r_region__val + r_country__val
    ) %>% 
    group_by(country, region) %>% 
    median_qi(internet, outcome)

  # Create country ellipse data
  country_ellipse <- spread_draws(
    fit,
    b_val_year, 
    b_internet_year,
    sd_country__val_year,
    sd_country__internet_year,
    cor_country__internet_year__val_year, 
    ndraws = 100
  ) %>% 
    rename(
      cor = cor_country__internet_year__val_year, 
      sd_outcome = sd_country__val_year,
      sd_i = sd_country__internet_year,
      b_outcome = b_val_year,
      b_i = b_internet_year
    ) %>% 
    mutate(
      e = pmap(
        list(cor, sd_outcome, sd_i, b_outcome, b_i), 
        function(cor, sd_a, sd_i, b_a, b_i) 
          ellipse(
            cor, 
            scale = c(sd_i, sd_outcome), 
            centre = c(b_i, b_outcome), 
            level = .90
          ) %>% 
          as_tibble()
      )
    ) %>% 
    unnest(e)

  # Correlation
  country_cor_result <- spread_draws(fit, cor_country__internet_year__val_year) %>% 
    median_qi(.width = .90) %>% 
    mutate(across(where(is.numeric), ~round(., 2))) %>%
    {str_glue("{.[,1]} [{.[,2]}, {.[,3]}]")}

@@

```{r}
draw_scatterplot(fits_1c$fit[[1]]) + labs(y = "Anxiety trend")
draw_scatterplot(fits_1c$fit[[2]]) + labs(y = "Depression trend")
draw_scatterplot(fits_1c$fit[[3]]) + labs(y = "Self-harm trend")
```

```{r}
p_time_main_correlations <- (p_cor_country_anx |
                               p_cor_country_dep |
                               p_cor_country_sel)

@@

@@

```{r}
fits_brm_internet_interactions %>% 
  mutate(
    out = map(
      fit, 
      ~as_draws(.x, variable = "b_", regex = TRUE) %>% 
        summarise_draws(quantile, rhat, .args = list(probs = c(.5, .05, .95)))
    )
  ) %>% 
  select(-fit) %>% 
  unnest(out) %>% 
  # filter(str_detect(variable, "_i1_cw|b$")) %>% 
  kbl(digits = 3) %>% 
  kable_minimal(full_width = FALSE)
```

### Forest plots

figure of coefficients forest plot

```{r}
anx_draws <- spread_draws(
  fit_anx, 
  b_i1_cw, r_region[region, term] | region
) %>% 
  filter(term == "i1_cw") %>% 
  ungroup() %>% 
  select(-term) %>% 
  rename(Average = b_i1_cw) %>% 
  mutate(outcome = "Anxiety")
dep_draws <- spread_draws(
  fit_dep, 
  b_i1_cw, r_region[region, term] | region
) %>% 
  filter(term == "i1_cw") %>% 
  ungroup() %>% 
  select(-term) %>% 
  rename(Average = b_i1_cw) %>% 
  mutate(outcome = "Depression")
sel_draws <- spread_draws(
  fit_sel, 
  b_i1_cw, r_region[region, term] | region
) %>% 
  filter(term == "i1_cw") %>% 
  ungroup() %>% 
  select(-term) %>% 
  rename(Average = b_i1_cw) %>% 
  mutate(outcome = "Selfharm")

results_text <- bind_rows(anx_draws, dep_draws, sel_draws) %>% 
  group_by(outcome) %>% 
  summarise(parameters(cur_data()[-c(1:3)])) %>% 
  mutate(region = str_replace(Parameter, "\\.", " ")) %>% 
  mutate(is_average = region == "Average") %>% 
  mutate(region = if_else(region=="Average", "**Average**", region)) %>% 
  mutate(across(Median:CI_high, ~format(round(., 2), nsmall = 2)))

p_internet_main_coefs <- bind_rows(anx_draws, dep_draws, sel_draws) %>% 
  mutate(across(Africa:Southern.Asia, ~.+Average)) %>% 
  pivot_longer(Average:Southern.Asia, names_to = "region") %>% 
  mutate(region = fct_relevel(factor(region), "Average")) %>% 
  mutate(outcome = factor(outcome)) %>% 
  mutate(is_average = region == "Average") %>% 
  mutate(region = str_replace(region, "\\.", " ")) %>% 
  mutate(region = if_else(region=="Average", "**Average**", region)) %>% 
  ggplot(aes(value, region, fill = is_average, alpha = is_average)) +
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
  scale_alpha_manual(values = c(.4, .8)) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_shape_manual(values = c(21, 19)) +
  scale_y_discrete(expand = expansion(c(0.01, .1))) +
  scale_x_continuous(
    "Magnitude of association between internet adoption and well-being", 
    breaks = pretty_breaks(), 
    expand = expansion(c(.1, .5))
  ) +
  stat_halfeye(
    point_interval = NULL, normalize = "panels", 
    height = .75, adjust = 1.5
  ) +
  stat_pointinterval(
    alpha = 1, .width = c(.9),
    interval_size = .5,
    point_size = 1.5,
    fill = "white",
    aes(shape = after_stat(xmin > 0 | xmax < 0)),
    position = position_nudge(0, -.025)
  ) +
  geom_text(
    data = results_text, alpha = 1, size = 2.75, hjust = 1, vjust = -0.2,
    aes(
      x = Inf, 
      label = str_glue("{Median} [{CI_low}, {CI_high}]")
    )
  ) +
  facet_wrap("outcome", nrow = 1, scales = "free_x") +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_markdown(),
    legend.position = "none"
  )

(wrap_elements(grid::textGrob('Negative experiences\nTBD')) |
    wrap_elements(grid::textGrob('Positive experiences\nTBD')) |
    wrap_elements(grid::textGrob('Life satisfaction\nTBD'))) /
  p_internet_main_coefs
```

### Figure: Between country effects

```{r}
pred_data <- gbd_wide %>% 
  distinct(region, country, sex, age, i1_cb, i1_cw = 0, time = 0) %>% 
  filter(country %in% sort(unique(fit_anx$data$country)))

tmp <- epred_draws(
  fit_anx, pred_data, re_formula = 
    ~(1 + time*sex + time*age + i1_cw*sex + i1_cw*age | region) + 
    (1 + time*sex + time*age + i1_cw*sex + i1_cw*age | country)
)

tmp %>% 
  group_by(region, country, i1_cb) %>% 
  summarise(mean(.epred))

conditional_effects(fit_anx, "i1_cb")

gbd_wide %>% 
  group_by(country) %>% 
  summarise(i1_cb = unique(i1_cb), anx = mean(Anxiety)) %>% 
  ggplot(aes(i1_cb, anx)) +
  geom_point() +
  stat_smooth()

filter(country %in% sort(unique(fit_anx$data$country))) %>% 
  mutate(time = 0) %>% 
  group_by(country) %>% 
  mutate(xmin = min(i1_cw, na.rm = TRUE), xmax = max(i1_cw, na.rm = TRUE)) %>% 
  filter(i1_cw %in% c(xmin, xmax)) %>% 
  ungroup()
```

### Sex and Age

```{r}
# Get some stuff and transform :)
get_draws <- function(fit) {
  draws_region <- spread_draws(
    fit, 
    b_i1_cw, `b_age1:i1_cw`, `b_sex1:i1_cw`,
    r_region[region, term] | term
  ) %>% 
    mutate(
      `15 to 19` = b_i1_cw + i1_cw + (`age1:i1_cw` + `b_age1:i1_cw`)*-0.5,
      `20 to 24` = b_i1_cw + i1_cw + (`age1:i1_cw` + `b_age1:i1_cw`)*0.5,
      Female = b_i1_cw + i1_cw + (`sex1:i1_cw` + `b_sex1:i1_cw`)*-0.5,
      Male = b_i1_cw + i1_cw + (`sex1:i1_cw` + `b_sex1:i1_cw`)*0.5,
      Age = `age1:i1_cw` + `b_age1:i1_cw`,
      Sex = `sex1:i1_cw` + `b_sex1:i1_cw`
    ) %>% 
    select(region, `15 to 19`:Sex)

  draws_avg <- spread_draws(
    fit, 
    b_i1_cw, `b_age1:i1_cw`, `b_sex1:i1_cw`
  ) %>% 
    mutate(
      `15 to 19` = b_i1_cw + `b_age1:i1_cw`*-0.5,
      `20 to 24` = b_i1_cw + `b_age1:i1_cw`*0.5,
      Female = b_i1_cw + `b_sex1:i1_cw`*-0.5,
      Male = b_i1_cw + `b_sex1:i1_cw`*0.5,
      Age = `b_age1:i1_cw`,
      Sex = `b_sex1:i1_cw`
    ) %>% 
    mutate(region = "**Average**") %>% 
    select(region, `15 to 19`:Sex)

  draws <- bind_rows(
    "regions" = draws_region,
    "average" = draws_avg, 
    .id = "Level"
  ) %>% 
    mutate(region = str_replace(region, "\\.", "\n")) %>% 
    ungroup()
  draws
}

draws <- bind_rows(
  "Anxiety" = get_draws(fit_anx),
  "Depression" = get_draws(fit_dep),
  "Selfharm" = get_draws(fit_sel),
  .id = "outcome"
)

draws_sum <- draws %>% 
  select(outcome, region, Age, Sex) %>% 
  group_by(outcome, region) %>% 
  summarise(
    describe_posterior(
      cur_data(), centrality = "mean", test = "pd"
    )
  ) %>% 
  rename(panel = Parameter) %>% 
  mutate(across(where(is.numeric), ~round(., 2)))

draws %>% 
  select(outcome, Level, region, `15 to 19`:Male) %>% 
  pivot_longer(-c(region, Level, outcome), names_to = "Group") %>% 
  mutate(panel = if_else(str_detect(Group, "ale"), "Sex", "Age")) %>% 
  mutate(
    side = if_else(Group %in% c("15 to 19", "Female"), "top", "bottom")
  ) %>% 
  mutate(region = str_replace(region, "\\.", " ")) %>% 
  mutate(region = fct_relevel(region, "**Average**")) %>% 
  ggplot(aes(value, region, col = Group, fill = Group)) +
  scale_alpha_manual(values = c(.6, .3)) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_shape_manual(
    values = c(21, 19), guide = "none"
    ) +
  scale_y_discrete(expand = expansion(c(0.1, 0.1))) +
  scale_x_continuous(
    "Magnitude of association between internet adoption and well-being", 
    breaks = pretty_breaks(), 
    expand = expansion(c(0, .05))
  ) +
  stat_halfeye(
    point_interval = NULL, normalize = "panels", 
    height = .75, adjust = 1.5,
    aes(side = side, group = side, alpha = Level), 
    show.legend = FALSE
  ) +
  stat_pointinterval(
    alpha = 1, .width = c(.9),
    interval_size = .33,
    point_size = 1.25,
    fill = "white",
    aes(shape = after_stat(xmin > 0 | xmax < 0), group = side),
    position = position_dodgev(.25), key_glyph = draw_key_point
  ) +
  geom_richtext(
    data = draws_sum %>% 
      mutate(Group = NA) %>% 
      filter(outcome %in% c("Anxiety", "Depression", "Selfharm")),
    aes(
      x = Inf, 
      label = str_glue("*d* = {Mean} (p<sup>d</sup> = {percent(pd, 1)})")
    ),
    size = 2.5, hjust = 1,
    family = Font,
    fill = NA, label.color = NA,
    show.legend = FALSE
  ) +
  facet_grid2(panel ~ outcome, scales = "free_x", axes = "x") +
  guides(
    alpha = "none"
  ) +
  theme(
    legend.position = "right",
    axis.title.y = element_blank(),
    axis.text.y = element_markdown()
  )
```

### Fitted lines

Plot of fitted lines
